Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-14 paper.tex
fill out conclusion a bit

@@

The impact of modeling assumptions depends heavily on the metrics of interest.
For example, someone interested in fuel-shortage driven reactor outages could
observe a factor of four span among the four cases shown in the detail
comparison.  However, someone more interested in the overall transition speed
would not see as significant a discrepancy.  Also notable is that these
different modeling choices may have varying levels of significance depending
on the scenario/context they are operating in.  Figure \ref{fig:puinv-compare}
shows the same inventory curves from Figure \ref{fig:puinv} superimposed.
Before the fuel shortage begins, differences between each of the four cases
are relatively minor.  However, after the shortage begins around year 100,
separated Pu inventories vary much more significantly between the different
cases.

>>>>

Also notable is that different modeling choices (e.g. time step duration,
facility discretization, etc.) may have varying levels of significance
depending on the scenario/context they are operating in.  Figure
\ref{fig:puinv-compare} shows the same inventory curves from Figure
\ref{fig:puinv} superimposed.  Before the fuel shortage begins, differences
between each of the four cases are relatively minor.  However, after the
shortage begins around year 100, separated Pu inventories vary much more
significantly between the different cases.

@@

The impact of modeling assumptions depends heavily on the metrics of interest.
For example, someone interested in fuel-shortage driven reactor outages could
observe a factor of four span among the four cases shown in the detail
comparison.  However, someone more interested in the overall transition speed
would not see as significant a discrepancy.

In an unconstrained supply setting, varying the time step duration or
discretization of facility modeling have a relatively minor impact on the
overall simulation results.  Differences become more significant in material
constrained regimes.  Robustness in constrained regimes is especially useful
in the context of sensitivity and optimization analysis.
